% 	Benjamin Van Durme, vandurme@cs.rochester.edu, 24 Aug 2009
%
% Purpose: an example .tex file for the thesis.
%
% This file was derived from those used by Ashwin Lall and Piotr Faliszewski in
% their respective thesis works.

\documentclass[11pt,leqno]{report}

% Feb 24, 2010 vandurme> I used a separate header.tex to capture personal
% shortcuts, and included packages. This allowed my to create mini-documents
% based on each chapter, by having a distinct top-level file around each of the
% files "\include"-ed below, that could each then use the same header (so
% changes would be kept in sync):
%
%\input{header}
%
% The first two things in that header:
%\usepackage{urcsbiblio}
%\usepackage{urcsthesis}

\pdfinfo{
/Title (Extracting Implicit Knowledge from Text)
/Author (Benjamin D. Van Durme)
/Keywords (thesis, knowledge acquisition, information extraction)
}

\begin{document}

\sloppy
\title{Extracting Implicit Knowledge from Text}
\author{Benjamin D. Van Durme}
%\thesissupervisor{Professor Lenhart K. Schubert}
\maketitle

% Feb 24, 2010 vandurme> the graduate office wanted a "ii" on the top right
% corner of the dedication page (lowercase Roman numeral page numbering), which
% explains the slightly messy tex code for this page:

%%%dedication page
\thispagestyle{empty}
%\thispagestyle{plain}
\newenvironment{dedication}
{\cleardoublepage \thispagestyle{empty} \vspace*{\stretch{1}}
  \begin{center} \em}
  {\end{center} \vspace*{\stretch{3}} }
\begin{dedication}

  %% To ... 

\end{dedication}

%%% CV page
%\begin{curriculumvitae}

  Benjamin David Van Durme was born in Dansville, New York on November~13th,
  1979. He began studies at the University of Rochester in 1997, graduating in
  2001 with a Bachelor of Arts degree in the area of Cognitive Science and a
  Bachelor of Science degree in the area of Computer Science. From 2002 to 2004,
  he attended Carnegie Mellon University, and graduated with a Master of Science
  degree in Language Technologies. Benjamin returned to the University of
  Rochester in the Fall of 2004, pursuing research in the subjects of Computer
  Science and Linguistics, under the direction of Professor Lenhart K. Schubert.
  He received the Master of Science degree in Computer Science from the
  University of Rochester in 2006. During the Summer of 2006, as well as 2007,
  Benjamin performed research at Google Inc., under the direction of Marius
  Pa\c{s}ca.

\end{curriculumvitae}

\begin{acknowledgments}

  To my committee as a whole, William Cohen, Gregory Carlson, Daniel Gildea, and
  Lenhart K. Schubert: thank you for your advice and guidance.

  %% Additional personal acknowledgments ...

  Chapter~\ref{ch:Framework} is the result of extensive discussions with Len
  Schubert on a variety of semantic phenomena. Chapter~\ref{ch:Methodology}
  derives from joint work with Len Schubert \cite{vandurmeSTEP08}.
  Chapter~\ref{ch:UsingClasses} is the result of joint work with Ting Qian and
  Len Schubert \cite{vandurmeCOLING08}. Material from
  Chapter~\ref{ch:LearningClasses} is based on collaboration with Marius
  Pa\c{s}ca while at Google Inc. \cite{vandurmeAAAI08}.
  Chapter~\ref{ch:UsingOntology} is based on joint work with Phillip Michalak
  and Len Schubert \cite{vandurmeEACL09}. Chapter~\ref{ch:TopicModels} is based
  on work performed with Dan Gildea \cite{vandurmeTR09}.

  This material is based upon research supported by National Science Foundations
  awards, IIS-0328849 entitled ``Deriving General World Knowledge from Texts by
  Abstraction of Logical Forms'', IIS-0535105 entitled ``Knowledge
  Representation and Reasoning Mechanisms for Explicitly Self-Aware
  Communicative Agents'' and CCF--0910415 entitled ``RI: Small: General
  Knowledge Bootstrapping from Text'', in addition to a University of Rochester
  Provost's Multidisciplinary Award (2008), entitled ``Computational
  Psycholinguistics: Integrating Computational and Behavioral Methods to Study
  Human Language Processing''. Any opinions, findings, and conclusions or
  recommendations expressed in this material are those of the author and do not
  necessarily reflect the views of above named organizations.

\end{acknowledgments}

\begin{abstract}

  The everyday intelligence of both humans and machines relies on a large store
  of background, or common-sense, knowledge. That such a knowledge base is not
  yet available to machines helps partially explain the community's inability to
  provide society with the sort of synthetic intelligence described by futurists
  such as Turing, or Asimov.

  In response, there have emerged a variety of methods for automated
  \emph{Knowledge Acquisition (KA)} that are now being actively explored. Here I
  consider the extraction of knowledge that is conveyed \emph{implicitly}, both
  within everyday texts and queries posed to internet search engines. Through
  recognizing certain forms of existential predicative patterns, and abstracting
  from these to more strongly quantifiable statements, I show that a significant
  amount of general knowledge can be gleaned based on how we talk about the
  world. I provide experimental results both for the direct extraction and
  strengthening of such knowledge, and for the automatic acquisition of
  supporting resources for this task.

  In addition, I draw attention to the relationship between automatically
  acquired background knowledge and natural language \emph{generic} sentences.
  Humans use generics when they wish to directly assert the same sorts of
  ``rules of the world'' that are of concern to the KA community. And yet, there
  has been little recognition in applied circles that decades of work from
  formal linguistic semantics may have a role to play in the representation, and
  perhaps even the acquisition, of common knowledge.
  
\end{abstract}

\tableofcontents
\listoftables
\listoffigures

\include{introduction}

\include{background}       
                         
\include{framework}        

\include{methodology}      

\include{using-classes}    

\include{learning-classes} 

\include{using-ontology}   

\include{topic-models}     

\include{conclusion}

\bibliographystyle{named}
\bibliography{references}

\appendix
\include{generics}


\end{document}



